We Are All Trying to Describe Something And We Don't Have the Words

### 2023-04-11 outputs/paper/paper.qmd
changed title, plotted danceability/energy quadrant

---
title: "Jack Antonoff-ification of pop music"
subtitle: "My subtitle if needed"
author: 
  - Michaela Drouillard
thanks: "Code and data are available at: LINK."
date: today
abstract: "In this essay, I will be exploring Jack Antonoff's production style using data from the Spotify API. Drawing from an interview with Caleb Gamman, a guy who went viral for guessing which song on Taylor Swift's Midnights album was produced by Antonoff within seconds, I will delve into the specific characteristics that define an Antonoff-y song, and assess whether or not the audio features defined by Spotify can capture this. I plan to lasso Glen McDonald,the Spotify engineer behind these features, into explaining them to me. There will be a Bayesian inference model. It will be a logistic regression. We do not know whether or not it will be good. Finally, I will armchair a little bit about the cultural significance of Antonoff's music and the reasons behind his ubiquity in the music industry."
format: pdf
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "We Are All Trying to Describe Something And We Don't Have the Words"
subtitle: "an exploration of the Jack Antonoffification of Pop Music"
author: 
  - Michaela Drouillard
thanks: "Code and data are available at: LINK."
date: today
abstract: "In this essay, I will be exploring Jack Antonoff's production style using data from the Spotify API. Drawing from an interview with Caleb Gamman, a guy who went viral for guessing which song on Taylor Swift's Midnights album was produced by Antonoff within seconds, I will delve into the specific characteristics that define an Antonoff-y song, and assess whether or not the audio features defined by Spotify can capture this. I plan to lasso Glen McDonald,the Spotify engineer behind these features, into explaining them to me. There will be a Bayesian inference model. It will be a logistic regression. We do not know whether or not it will be good. Finally, I will armchair a little bit about the cultural significance of Antonoff's music and the reasons behind his ubiquity in the music industry."
format: pdf
number-sections: true
bibliography: references.bib
---
